Analysis plan

### 2023-03-16 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Added some details on how to assign employees to teams, and how to define a team

The analysis will be done for staff and teams separately and aggregated
independently. The table below defines how we plan to aggregate for
staff and teams.

@@

-   Indicator for a switch in supervisor

@@

@@

>>>>

The analysis will be done for staff and teams separately and aggregated
independently. Employees will be categorized. Also, employees with be grouped into teams based on supervisor. These teams will also be categorized.  The table below defines how we plan to aggregate for
staff and teams.

@@

-   Number of supervisors

@@

Teams will be defined based on the supervisors in March 2022. The unique identifier for teams will be the `supervisor_e_mail_address`. All employees under those supervisors will be defined as part of the team. Employees may join and leave a team over the observation window.

@@

-   Total employees in team over observation window
